>

### 2019-04-22 paper/spinifex-paper.tex
revised title and abstrsact

% !TeX root = RJwrapper.tex
\title{spinifex: A Package for Manual Control of Dynamic Linear Projections of
Multivariate Data}
\author{by Nicholas Spyrison, Dianne Cook}

@@

\abstract{%
The set of dynamic linear projections of multivariate data collectively
known as \textbf{tours} provides an important tool for extending the
dimensionality of visuals. The R package \textbf{tourr} offers a variety
of path generators and geometric displays for conducting tours. This
paper discusses an extension package, \textbf{spinifex}, that adds
support for the path generation of manual tours and extends the display
of tours to use with the animation packages, \textbf{plotly} and
\textbf{gganimate}. Manual tours are used to explore the sensitivity of
structure as the contributions of a manipulation variable are changed. A
recent paper (Wang et al.
\protect\hyperlink{ref-wang_mapping_2018}{2018}) visualized the
sensitivity of the hadronic experiments to nucleon structure.
Sensitivity was characterized in non-linear 3D embeddings of the first
10 principal components. This research applies manual tours to this data
showing that manual tours resolve information about the structure of
cluster distribution by bringing revealing information that is
orthogonal to static viewing planes.
}

@@

\address{%
Dianne Cook\\
Monash University\\
Department of Econometrics and Business Statistics\\
}
\href{mailto:DiCook@monash.edu}{\nolinkurl{DiCook@monash.edu}}

>>>>

% !TeX root = RJwrapper.tex
\title{spinifex: A Package for Creating an Animation of a Manually Controlled
Tour of Linear Projections of Multivariate Data, to Explore the
Sensitivity of Structure to Specific Variables}
\author{by Nicholas Spyrison, Dianne Cook}

@@

\abstract{%
Dynamic linear projections of multivariate data collectively known as
\textbf{tours} provide an important tool for exploring mulitvariate data
and models. The R package \textbf{tourr} provides functions for several
types of tours: grand, guided, little, local and frozen. Each of these
can be viewed dynamically, or saved into a data object for animation.
This paper describes a new package, \textbf{spinifex}, to provide a
manual tour, that allows the coefficient for a single variable to be
varied, with the result displayed using animation, with the packages,
\textbf{plotly} and \textbf{gganimate}. By varying the coefficient of a
single variable, it is possible to explore the sensitivity of structure
in the projection to that variable. It is particularly useful when used
with a projection pursuit guided tour to simplify and understand the
solution. The manual tour is applied to a problem from particle physics.
}

@@

\address{%
Dianne Cook\\
Monash University\\
Department of Econometrics and Business Statistics\\
}
\href{mailto:dicook@monash.edu}{\nolinkurl{dicook@monash.edu}}

### 2019-04-22 paper/spinifex_paper.Rmd
revised title and abstrsact

---
title: > 
  spinifex: A Package for Manual Control of Dynamic Linear Projections of Multivariate Data
author:
  - name: Nicholas Spyrison
    affiliation: Monash University 
    address:
    - Faculty of Information Technology
    email:  Nicholas.Spyrison@monash.edu
  - name: Dianne Cook
    affiliation: Monash University 
    address:
    - Department of Econometrics and Business Statistics
    email:  DiCook@monash.edu
abstract: >
  The set of dynamic linear projections of multivariate data collectively known as **tours** provides an important tool for extending the dimensionality of visuals. The R package **tourr** offers a variety of path generators and geometric displays for conducting tours. This paper discusses an extension package, **spinifex**, that adds support for the path generation of manual tours and extends the display of tours to use with the animation packages, **plotly** and **gganimate**. Manual tours are used to explore the sensitivity of structure as the contributions of a manipulation variable are changed.

  A recent paper [@wang_mapping_2018] visualized the sensitivity of the hadronic experiments to nucleon structure. Sensitivity was characterized in non-linear 3D embeddings of the first 10 principal components. This research applies manual tours to this data showing that manual tours resolve information about the structure of cluster distribution by bringing revealing information that is orthogonal to static viewing planes.
keywords: manual tour, guided tour, grand tour, projection pursuit, high dimensional data, multivariate data, data visualization, statistical graphics, data science
preamble: >
  % preamble packages
link-citations: true
fig_caption: yes
toc: false
bibliography: spinifex_paper.bib
output: rticles::rjournal_article
  #bookdown::pdf_book:
   # base_format: rticles::rjournal_article #see sandbox for hard code solution.
---
\bibliography{spinifex_paper}
<!-- note that Di/Ursula have different setup and options and use static images.  -->
```{r setup_paper, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", echo = TRUE, collapse = TRUE,
  message = FALSE, warning = FALSE, error = FALSE,
  cache = F, cache.lazy = FALSE
)
library(spinifex)
library(ggplot2)
```

>>>>

---
title: > 
  spinifex: A Package for Creating an Animation of a Manually Controlled Tour of Linear Projections of Multivariate Data, to Explore the Sensitivity of Structure to Specific Variables
author:
  - name: Nicholas Spyrison
    affiliation: Monash University 
    address:
    - Faculty of Information Technology
    email:  Nicholas.Spyrison@monash.edu
  - name: Dianne Cook
    affiliation: Monash University 
    address:
    - Department of Econometrics and Business Statistics
    email:  dicook@monash.edu
abstract: >
  Dynamic linear projections of multivariate data collectively known as **tours** provide an important tool for exploring mulitvariate data and models. The R package **tourr** provides functions for several types of tours: grand, guided, little, local and frozen. Each of these can be viewed dynamically, or saved into a data object for animation. This paper describes a new package, **spinifex**, to provide a manual tour, that allows the coefficient for a single variable to be varied, with the result displayed using animation, with the packages, **plotly** and **gganimate**. By varying the coefficient of a single variable, it is possible to explore the sensitivity of structure in the projection to that variable. It is particularly useful when used with a projection pursuit guided tour to simplify and understand the solution. The manual tour is applied to a problem from particle physics.

keywords: exploratory data anlaysis, projection pursuit, high dimensional data, data visualization, statistical graphics, data science
preamble: >
  % preamble packages
link-citations: true
fig_caption: yes
toc: false
bibliography: spinifex_paper.bib
output: rticles::rjournal_article
  #bookdown::pdf_book:
   # base_format: rticles::rjournal_article #see sandbox for hard code solution.
---
\bibliography{spinifex_paper}
<!-- note that Di/Ursula have different setup and options and use static images.  -->
```{r setup_paper, include=FALSE}
knitr::opts_chunk$set(
  fig.align = "center", echo = TRUE, collapse = TRUE,
  message = FALSE, warning = FALSE, error = FALSE,
  cache = F, cache.lazy = FALSE
)
library(spinifex)
library(ggplot2)
```
